Detection of an Intrinsic Color Parameter within the Type~Ia Supernovae of the Nearby Supernova Factory

### 2016-09-12 forgerard.tex
a stable version before vacation

\begin{abstract}
An empirical model for SN~Ia peak magnitudes with two color parameters and dependence on the equivalent widths of CaII, SiII, and SiII velocity
is applied to the supernova sample of the Nearby Supernova Factory.  The peak magnitudes and their colors are found to be 
dependent on the spectral equivalent widths, and two independent color parameters with better than 0.999 confidence.
One parameter, interpreted as due to extrinsic host-galaxy
dust extinction, is consistent with an $R_V=3.06$  \citet{1999PASP..111...63F} dust model.  The second parameter is inconsistent with dust and
is inferred to have origins intrinsic to supernovae.  Our model explains features of external data: 
\textcolor{red}{
the wide range of inferred $R_V$ among
SNe~Ia, the systematically lower $R_V$ of redder supernovae relative to the upper bound of the full population,} and the colors of SN~2014J.
\end{abstract}

@@

Supernova-frame synthetic photometry is generated for the top-hat filter system
described in \citet{2011A&A...529L...4C}, which is comprised of five logarithmically-spaced bands spanning
3276--8635 \AA; the bands have approximate correspondence to $UBVRI$ and are thus referred to as such.
For each supernova, the magnitudes at peak brightness are determined using single-band SALT2 fits.
The equivalent widths of SiII$\lambda 4141$ and the CaII H\&K features are computed as
in \citet{2008A&A...477..717B} and the  velocity of SiII$\lambda 6355$ (expressed as the
observed location of the feature $\lambda_{Si} = (1+v_{Si}/c) 6355$\AA)
as in \citet{chotard:thesis}.
Equivalent widths with 2.5 days of maximum are considered, in the case of multiple spectra the one
closest to maximum is used \citep{chotard:thesis}. [Confirm!]
The weighted mean from phases within 3 days of maximum light is used for the  SiII$\lambda 6355$ velocity.

@@

We assume 
that  peak intrinsic $UBVRI$ magnitudes are linearly dependent
on the equivalent widths of the CaII H\&K and SiII$\lambda$4141 spectral features
$EW_{Ca}$, $EW_{Si}$,
the SiII$\lambda6355$ position $\lambda_{Si}$ (so also linear with $v_{Si}$):
these spectral features are associated with SN~Ia  spectroscopic diversity  
\citep{2006PASP..118..560B,2009A&A...500L..17B, 2009PASP..121..238B, 2009ApJ...699L.139W, 2011ApJ...729...55F}.
$EW_{Si}$ at peak brightness is an effective proxy for the light-curve shape parameter
\citep{2011A&A...529L...4C}. 
An intrinsic-color parameter $D$ describes  intrinsic magnitude/color variation unaccounted for by the spectral features.
Residual dispersion is described by a Normal distribution with a parameterized covariance matrix
$C_c$.  A grey magnitude offset $\Delta$ is included for each supernova
to capture intrinsic dispersion and peculiar-velocity errors introduced when converting fluxes to luminosity.
The observed magnitudes are linearly dependent on an
extrinsic-color parameter $k$.  The observables
$U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $v_{Si,o}$
shown in Table~\ref{data:tab} have Gaussian measurement uncertainty with covariance $C$.
The model is written as
\begin{equation}
\begin{pmatrix}
U\\B\\V\\R\\I
\end{pmatrix}
\sim \mathcal{N}
\left(
\Delta +
\begin{pmatrix}
c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 \lambda_{Si} + \delta_0 D\\
c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 \lambda_{Si} + \delta_1 D \\
c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 \lambda_{Si} + \delta_2 D\\
c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 \lambda_{Si} + \delta_3 D\\
c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 \lambda_{Si} + \delta_4 D
\end{pmatrix}
,C_{c}
\right)
\label{ewsiv:eqn}
\end{equation}
\begin{equation}
\begin{pmatrix}
U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ v_{Si, o}
\end{pmatrix}
\sim \mathcal{N}
\left(
\begin{pmatrix}
U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
\end{pmatrix}
,C
\right).
\label{dust:eqn}
\end{equation}
The global parameters $c$, $\alpha$, $\beta$, $\eta$, and $\delta$  are the intercepts and slopes of the linear relationships that
relate intrinsic magnitudes with the spectral-feature parameters and intrinsic-color parameter.
(In this article we freely interchange the parameter indices with  $01234$ or $UBVRI$.)
The global parameters $\gamma$ are the slopes that connect the extrinsic-color
parameter and observed magnitudes.  To constrain the degrees of freedom and degeneracies inherent in the model we impose
\begin{equation}
\langle \Delta \rangle=0, \langle k \rangle=0, \langle D \rangle=0, \gamma_0 > 0, \delta_0 < 0.
\end{equation}
The first two specify the definition of zero color relative to which the color excess is measured.    The latter two exclude degenerate posterior space
associated
with  simultaneous sign flips of
$\delta$--$D$ and $\gamma$--$k$.
\color{red}
We assign $k$ and $D$ identical initial conditions, so the difference in the signs of $\gamma_0$ and $\delta_0$ is non-trivial.
Although not formally a degeneracy in the model, practically the parameter pairs  $\delta$--$D$ and $\gamma$--$k$ are degenerate with
each other, as is apparent after 
running the Monte Carlo with exchange of the initial  and boundary conditions of $\delta$ and $\gamma$.
The different initial and boundary conditions for $\gamma_0$ and $\delta_0$ break the degeneracy of our mixture model;
otherwise identical initial conditions for $\gamma$, $\delta$ give them identical posteriors
with broader credible intervals and lower maximum likelihood than when the initial conditions are different.
\color{black}
As the model cannot distinguish which effect is intrinsic or extrinsic, we do so
by assigning the parameters whose values are consistent with dust to $\gamma$ and the others to $\delta$.

@@

The differences between observed colors and the colors predicted from the analysis are shown in Figure~\ref{residual:fig}.
There are no apparent systematic trends over the span of colors.  The intrinsic color dispersions from our model are described
later in our discussion of the inferred $C_c$.
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5in]{output11/residual.pdf} 
            \caption{\textcolor{red}{Differences between observed colors and the colors predicted from the analysis, as a function
            of predicted colors.  For reference a dotted line is plotted at zero difference.}
            \label{residual:fig}}
\end{figure}

@@

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
& $X=0$ &1&2&3&4\\ \hline
$\alpha_{X}$
&
$0.0042^{0.0009}_{-0.0009}$
&
$0.0014^{0.0007}_{-0.0008}$
&
$0.0014^{0.0006}_{-0.0006}$
&
$0.0014^{0.0005}_{-0.0005}$
&
$0.0025^{0.0005}_{-0.0005}$
\\
$\alpha_X/\alpha_2-1$
&
$   2.0^{   1.3}_{  -0.6}$
&
$   0.0^{   0.1}_{  -0.2}$
&
0
&
$   0.0^{   0.2}_{  -0.1}$
&
$   0.8^{   0.9}_{  -0.4}$
\\
$\beta_{X}$
&
$ 0.033^{ 0.003}_{-0.003}$
&
$ 0.027^{ 0.003}_{-0.003}$
&
$ 0.027^{ 0.002}_{-0.002}$
&
$ 0.021^{ 0.002}_{-0.002}$
&
$ 0.020^{ 0.002}_{-0.002}$
\\
$\beta_X/\beta_2-1$
&
$  0.26^{  0.05}_{ -0.05}$
&
$  0.00^{  0.03}_{ -0.03}$
&
0
&
$ -0.19^{  0.01}_{ -0.01}$
&
$ -0.25^{  0.03}_{ -0.03}$
\\
$\eta_{X}$
&
$0.0010^{0.0012}_{-0.0013}$
&
$0.0006^{0.0010}_{-0.0011}$
&
$0.0008^{0.0008}_{-0.0009}$
&
$0.0008^{0.0007}_{-0.0008}$
&
$0.0002^{0.0006}_{-0.0007}$
\\
$\eta_X/\eta_2-1$
&
$  0.26^{  0.65}_{ -0.65}$
&
$ -0.09^{  0.53}_{ -0.55}$
&
0
&
$ -0.08^{  0.24}_{ -0.21}$
&
$ -0.57^{  0.51}_{ -0.59}$
\\
$\gamma_X/\gamma_2-1$
&
$  0.64^{  0.05}_{ -0.05}$
&
$  0.34^{  0.03}_{ -0.03}$
&
0
&
$ -0.23^{  0.01}_{ -0.01}$
&
$ -0.45^{  0.03}_{ -0.03}$
\\
$R_{X}$
&
$  4.87^{  0.48}_{ -0.43}$
&
$  3.96^{  0.40}_{ -0.35}$
&
$  2.96^{  0.31}_{ -0.28}$
&
$  2.29^{  0.26}_{ -0.23}$
&
$  1.64^{  0.21}_{ -0.19}$
\\
$\delta_X/\delta_2-1$
&
$-0.393^{ 0.182}_{-0.208}$
&
$-0.224^{ 0.101}_{-0.117}$
&
0
&
$-0.056^{ 0.051}_{-0.046}$
&
$-0.147^{ 0.096}_{-0.089}$
\\
$R_{\delta X}$
&
$ -2.70^{  1.32}_{ -2.44}$
&
$ -3.46^{  1.29}_{ -2.65}$
&
$ -4.46^{  1.43}_{ -3.11}$
&
$ -4.20^{  1.32}_{ -2.89}$
&
$ -3.80^{  1.20}_{ -2.61}$
\\
$\sigma_{X}$
&
$ 0.059^{ 0.012}_{-0.011}$
&
$ 0.031^{ 0.007}_{-0.007}$
&
$ 0.020^{ 0.004}_{-0.006}$
&
$ 0.013^{ 0.007}_{-0.008}$
&
$ 0.043^{ 0.005}_{-0.004}$
\\
\hline
\end{tabular}
\caption{68\% credible Intervals for the Global Fit Parameters \label{global:tab}}
\end{table}

@@

In the fit to our model, the observed color excess is attributed to   extrinsic
$E_\gamma(B-V)=  0.86 \pm   0.08$ and intrinsic $E_\delta(B-V)=  0.35 \pm   0.10$ contributions.
Among the supernovae in the SNfactory  set used to determine $\gamma$ and $\delta$, the
\color{red}
extreme median values for 
$E_\gamma(B-V)$ are $-0.07 \pm 0.01$ and  $  0.33 \pm 0.04$,
and for $E_\delta(B-V)$ $-0.01 \pm 0.01$  and
$  0.07 \pm 0.03$ 
\color{black}
(see Figure~\ref{ebv:fig}).
\textcolor{red}{In both parameters (which are relative to SN~2011fe), SN~2014J lives well outside the 
span} of supernovae used to train the coefficients of the model.

@@

\color{red}
Our model does not explicitly include light-curve shape, which is known to track SN~Ia diversity.
The correlation between $EW_{Si}$ and the SALT2 $X_1$ light-curve shape parameter is verified
for our sample, as shown in Figure~\ref{x1:fig}.
On the other hand, there is no such correlation seen between $E_\delta(B-V)$ and $X_1$. 
Our magnitude residuals  given in Eqn.~\ref{mag_cov:eqn} are comparable to those of SALT2
\citep[Fig.\ 8 of][]{2010A&A...523A...7G}, showing no obvious disadvantage from not using $X_1$.
Figure~\ref{x1res:fig} shows the difference between observed and model-predicted colors,
as a function of $X_1$.  For all colors, there appear non-linear correlations between $X_1$ and color residuals,
with a negative slope for $X_1<0$ and positive slope for $X_1>0$.
The SN~Ia time evolution does convey information not captured by the peak-magnitude spectral features used in
the current analysis, and  a linear model may be incapable of doing so.
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output11/x1si.pdf}
   \includegraphics[width=2.8in]{output11/x1D.pdf}
    \caption{\textcolor{red}{Left: SALT2 $X_1$ versus $EW_{Si}$.  Right: $X_1$ versus $E_\delta(B-V)$.}
   \label{x1:fig}}
\end{figure}

@@

@@

\color{red}
The extrinsic parameters $\gamma$ attributed to dust are fit for without reference to a specific dust model.
The posteriors of $\gamma$ are fit to the dust model of \citet{1999PASP..111...63F}, giving
$R^F_V=3.06\pm 0.18$;  Figure~\ref{fitz:fig} shows the   68\% credible intervals of $\gamma$ and the
result of the fit.  Note that  unlike the $R_V$ posteriors, 
the posteriors of $\gamma$ are well-approximated by a normal distribution, which is used for the fit.
\color{black}

>>>>

\begin{abstract}
An empirical model for SN~Ia peak magnitudes with two color parameters and dependence on the equivalent widths of CaII, SiII, and SiII velocity
is applied to the supernova sample of the Nearby Supernova Factory.  The peak magnitudes and their colors are found to be 
dependent on the spectral equivalent widths, and two independent color parameters with better than 0.999 confidence.
One parameter, interpreted as due to extrinsic host-galaxy
dust extinction, is consistent with an $R_V=3.06$  \citet{1999PASP..111...63F} dust model.  The second parameter is inconsistent with dust and
is inferred to have origins intrinsic to supernovae.  Our model explains features of external data: 
\textcolor{red}{
the wide range of inferred $R_V$ among
SNe~Ia, the systematically lower inferred $R_V$ of redder supernovae relative to the upper bound of the full population,} and the colors of SN~2014J.
\end{abstract}

@@

Supernova-frame synthetic photometry is generated for a top-hat filter system
comprised of five 
\color{red}
bands with the following wavelength ranges: $U$ $[3300.00 - 3978.02]$\AA;
$B$ $[3978.02-4795.35]$\AA;
$V$ $[4795.35-5780.60]$\AA;
$R$ $[5780.60-6968.29]$\AA;
$I$ $[6968.29-8400.00]$\AA.
\color{black}
For each supernova, the magnitudes at peak brightness are determined using single-band SALT2 fits.
The equivalent widths of SiII$\lambda 4141$ and the CaII H\&K features are computed as
in \citet{2008A&A...477..717B} and the  velocity of SiII$\lambda 6355$ (expressed as the
observed location of the feature $\lambda_{Si} = (1+v_{Si}/c) 6355$\AA)
as in \citet{chotard:thesis}.
Equivalent widths with 2.5 days of maximum are considered, in the case of multiple spectra the one
closest to maximum is used \citep{chotard:thesis}. [Confirm!]
The weighted mean from phases within 3 days of maximum light is used for the  SiII$\lambda 6355$ velocity.

@@

We assume 
that  peak intrinsic $UBVRI$ magnitudes are linearly dependent
on the equivalent widths of the CaII H\&K and SiII$\lambda$4141 spectral features
$EW_{Ca}$, $EW_{Si}$,
the SiII$\lambda6355$ position $\lambda_{Si}$ (so also linear with $v_{Si}$):
these spectral features are associated with SN~Ia  spectroscopic diversity  
\citep{2006PASP..118..560B,2009A&A...500L..17B, 2009PASP..121..238B, 2009ApJ...699L.139W, 2011ApJ...729...55F}.
$EW_{Si}$ at peak brightness is an effective proxy for the light-curve shape parameter
\citep{2011A&A...529L...4C}. 
An intrinsic-color parameter $D$ describes  intrinsic magnitude/color variation unaccounted for by the spectral features.
Residual dispersion is described by a Normal distribution with a parameterized covariance matrix
$C_c$.  A grey magnitude offset $\Delta$ is included for each supernova
to capture intrinsic dispersion and peculiar-velocity errors introduced when converting fluxes to luminosity.
The observed magnitudes are linearly dependent on an
extrinsic-color parameter $k$.  The observables
$U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$, $EW_{Si,o}$, $v_{Si,o}$
shown in Table~\ref{data:tab} have Gaussian measurement uncertainty with covariance $C$.
The model is written as
\begin{equation}
\begin{pmatrix}
U\\B\\V\\R\\I
\end{pmatrix}
\sim \mathcal{N}
\left(
\Delta +
\begin{pmatrix}
c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 \lambda_{Si} + \delta_0 D\\
c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 \lambda_{Si} + \delta_1 D \\
c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 \lambda_{Si} + \delta_2 D\\
c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 \lambda_{Si} + \delta_3 D\\
c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 \lambda_{Si} + \delta_4 D
\end{pmatrix}
,C_{c}
\right)
\label{ewsiv:eqn}
\end{equation}
\begin{equation}
\begin{pmatrix}
U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ v_{Si, o}
\end{pmatrix}
\sim \mathcal{N}
\left(
\begin{pmatrix}
U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
\end{pmatrix}
,C
\right).
\label{dust:eqn}
\end{equation}
The global parameters $c$, $\alpha$, $\beta$, $\eta$, and $\delta$  are the intercepts and slopes of the linear relationships that
relate intrinsic magnitudes with the spectral-feature parameters and intrinsic-color parameter.
(In this article we freely interchange the parameter indices with  $01234$ or $UBVRI$.)
The global parameters $\gamma$ are the slopes that connect the extrinsic-color
parameter and observed magnitudes.  To constrain the degrees of freedom and degeneracies inherent in the model we impose that
each of the vectors $k+1/N$ and $D+1/N$ are simplexes, where $N$ are the number of objects in our sample: these
conditions break the 
degeneracies  $\gamma \rightarrow a\gamma$, $k \rightarrow a^{-1}k$ and $\delta \rightarrow a\delta$, $D \rightarrow a^{-1}D$.
Furthermore we impose
\begin{equation}
\langle \Delta \rangle=0, \langle k \rangle=0, \langle D \rangle=0, \gamma_0 > 0, \delta_0 < 0.
\end{equation}
The first two specify the definition of zero color relative to which the color excess is measured.    The latter two exclude degenerate posterior space
associated
with  simultaneous sign flips of
$\delta$--$D$ and $\gamma$--$k$
(when running our fits, $k$ and $D$ are set to
identical initial conditions, so the difference in the signs of $\gamma_0$ and $\delta_0$ is non-trivial.)
Although not formally a degeneracy in the model, practically the parameter pairs  $\delta$--$D$ and $\gamma$--$k$ are degenerate with
each other, as is apparent after 
running the Monte Carlo with exchange of the initial  and boundary conditions of $\delta$ and $\gamma$.
The different initial and boundary conditions for $\gamma_0$ and $\delta_0$ break the degeneracy of our mixture model;
otherwise identical initial conditions for $\gamma$, $\delta$ produce indistinguishable posteriors
with relatively broader credible intervals and lower maximum likelihood.
As the model cannot distinguish which effect is intrinsic or extrinsic, we do so
by assigning the parameters whose values are consistent with dust to $\gamma$ and the others to $\delta$.

@@

The differences between observed and model-predicted supernova colors are shown in Figure~\ref{residual:fig}:
no systematic trends are apparent (in \S\ref{discussion:sec} we look for trends with light-curve shape.) 
The scatters in the plots, i.e.\ the residual intrinsic color dispersions from our model, are described
later when we discuss the inferred $C_c$.
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5in]{output11/residual.pdf} 
            \caption{\textcolor{red}{Differences between observed and  model-predicted supernova colors  as a function
            of predicted colors.  For reference a dotted line is plotted at zero difference.}
            \label{residual:fig}}
\end{figure}

@@

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
& $X=0$ &1&2&3&4\\ \hline
$\alpha_{X}$
&
$0.0042^{0.0009}_{-0.0009}$
&
$0.0014^{0.0007}_{-0.0008}$
&
$0.0014^{0.0006}_{-0.0006}$
&
$0.0014^{0.0005}_{-0.0005}$
&
$0.0025^{0.0005}_{-0.0005}$
\\
$\alpha_X/\alpha_2-1$
&
$   2.0^{   1.3}_{  -0.6}$
&
$   0.0^{   0.1}_{  -0.2}$
&
0
&
$   0.0^{   0.2}_{  -0.1}$
&
$   0.8^{   0.9}_{  -0.4}$
\\
$\beta_{X}$
&
$ 0.033^{ 0.003}_{-0.003}$
&
$ 0.027^{ 0.003}_{-0.003}$
&
$ 0.027^{ 0.002}_{-0.002}$
&
$ 0.021^{ 0.002}_{-0.002}$
&
$ 0.020^{ 0.002}_{-0.002}$
\\
$\beta_X/\beta_2-1$
&
$  0.26^{  0.05}_{ -0.05}$
&
$  0.00^{  0.03}_{ -0.03}$
&
0
&
$ -0.19^{  0.01}_{ -0.01}$
&
$ -0.25^{  0.03}_{ -0.03}$
\\
$\eta_{X}$
&
$0.0010^{0.0012}_{-0.0013}$
&
$0.0006^{0.0010}_{-0.0011}$
&
$0.0008^{0.0008}_{-0.0009}$
&
$0.0008^{0.0007}_{-0.0008}$
&
$0.0002^{0.0006}_{-0.0007}$
\\
$\eta_X/\eta_2-1$
&
$  0.26^{  0.65}_{ -0.65}$
&
$ -0.09^{  0.53}_{ -0.55}$
&
0
&
$ -0.08^{  0.24}_{ -0.21}$
&
$ -0.57^{  0.51}_{ -0.59}$
\\
$\gamma_X/\gamma_2-1$
&
$  0.64^{  0.05}_{ -0.05}$
&
$  0.34^{  0.03}_{ -0.03}$
&
0
&
$ -0.23^{  0.01}_{ -0.01}$
&
$ -0.45^{  0.03}_{ -0.03}$
\\
$R_{X}$
&
$  4.87^{  0.48}_{ -0.43}$
&
$  3.96^{  0.40}_{ -0.35}$
&
$  2.96^{  0.31}_{ -0.28}$
&
$  2.29^{  0.26}_{ -0.23}$
&
$  1.64^{  0.21}_{ -0.19}$
\\
$\delta_X/\delta_2-1$
&
$ -0.39^{  0.18}_{ -0.21}$
&
$ -0.22^{  0.10}_{ -0.12}$
&
0
&
$ -0.06^{  0.05}_{ -0.05}$
&
$ -0.15^{  0.10}_{ -0.09}$
\\
$R_{\delta X}$
&
$ -2.70^{  1.32}_{ -2.44}$
&
$ -3.46^{  1.29}_{ -2.65}$
&
$ -4.46^{  1.43}_{ -3.11}$
&
$ -4.20^{  1.32}_{ -2.89}$
&
$ -3.80^{  1.20}_{ -2.61}$
\\
$\sigma_{X}$
&
$ 0.059^{ 0.012}_{-0.011}$
&
$ 0.031^{ 0.007}_{-0.007}$
&
$ 0.020^{ 0.004}_{-0.006}$
&
$ 0.013^{ 0.007}_{-0.008}$
&
$ 0.043^{ 0.005}_{-0.004}$
\\
\hline
\end{tabular}
\caption{68\% credible Intervals for the Global Fit Parameters \label{global:tab}}
\end{table}

@@

In the fit to our model, the observed color excess is attributed to   extrinsic
$E_\gamma(B-V)=  0.86 \pm   0.08$ and intrinsic $E_\delta(B-V)=  0.35 \pm   0.10$ contributions.
Among the supernovae in the SNfactory  set used to determine $\gamma$ and $\delta$, the
\color{red}
extreme median values for 
$E_\gamma(B-V)$ are $-0.07 \pm 0.01$ and  $  0.33 \pm 0.04$,
and for $E_\delta(B-V)$ $-0.01 \pm 0.01$  and
$  0.07 \pm 0.03$ 
\color{black}
(see Figure~\ref{ebv:fig}).
\textcolor{red}{The deduced parameters for SN~2014J, which are relative to SN~2011fe, live well outside the 
span} of supernovae used to train the coefficients of the model.

@@

\color{red}
Our model does not explicitly include light-curve shape, which is known to track SN~Ia diversity.
The correlation between $EW_{Si}$ and the SALT2 $X_1$ light-curve shape parameter is verified
for our sample, as shown in Figure~\ref{x1:fig}.
On the other hand, there is no such correlation seen between $E_\delta(B-V)$ and $X_1$. 
Our magnitude residuals $\sigma_X$ are comparable to those of SALT2
\citep{2010A&A...523A...7G}, suffering no  disadvantage from the neglect of $X_1$.
Figure~\ref{x1res:fig} shows the difference between observed and model-predicted colors,
as a function of $X_1$: for all colors, there appear non-linear correlations 
with a negative slope for $X_1<0$ and positive slope for $X_1>0$.
We  run an extension of our model to include light-curve shape by adding a new linear term $\zeta X_1$; the credible intervals
from this analysis are given in Table~\ref{globalx1:tab}.  
The $\sigma_X$ values decrease at the per-mil level and there $<1\sigma$
shifts in parameters as compared to the previous results. 
The light-curve shape is not a strong predictor of supernova magnitude relative to the spectral features: the most significant non-zero values for
$\zeta$ are in the $V$ and $I$ bands at less than $1.5 \sigma$, while the $\alpha$'s and $\beta$'s remain significantly
non-zero.  This finding could be due to a deficiency of our model, 
as it  is incapable of capturing the non-linear trends in $X_1$ in Figure~\ref{x1res:fig}.
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output11/x1si.pdf}
   \includegraphics[width=2.8in]{output11/x1D.pdf}
    \caption{\textcolor{red}{Left: SALT2 $X_1$ versus $EW_{Si}$.  Right: $X_1$ versus $E_\delta(B-V)$.}
   \label{x1:fig}}
\end{figure}

@@

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
& $X=0$ &1&2&3&4\\ \hline
$\alpha_{X}$
&
$0.0039^{0.0010}_{-0.0010}$
&
$0.0013^{0.0008}_{-0.0008}$
&
$0.0015^{0.0007}_{-0.0007}$
&
$0.0014^{0.0006}_{-0.0006}$
&
$0.0026^{0.0005}_{-0.0005}$
\\
${\alpha_X/\alpha_2-1}$
&
$   1.6^{   1.1}_{  -0.5}$
&
$  -0.1^{   0.2}_{  -0.3}$
&
0
&
$  -0.1^{   0.1}_{  -0.1}$
&
$   0.8^{   0.9}_{  -0.4}$
\\
$\beta_{X}$
&
$ 0.036^{ 0.005}_{-0.005}$
&
$ 0.027^{ 0.004}_{-0.004}$
&
$ 0.023^{ 0.004}_{-0.004}$
&
$ 0.020^{ 0.003}_{-0.003}$
&
$ 0.017^{ 0.003}_{-0.003}$
\\
${\beta_X/\beta_2-1}$
&
$  0.56^{  0.12}_{ -0.10}$
&
$  0.18^{  0.06}_{ -0.06}$
&
0
&
$ -0.13^{  0.03}_{ -0.02}$
&
$ -0.29^{  0.06}_{ -0.06}$
\\
$\eta_{X}$
&
$0.0013^{0.0012}_{-0.0012}$
&
$0.0009^{0.0010}_{-0.0010}$
&
$0.0011^{0.0008}_{-0.0008}$
&
$0.0010^{0.0007}_{-0.0007}$
&
$0.0004^{0.0006}_{-0.0006}$
\\
${\eta_X/\eta_2-1}$
&
$  0.23^{  0.49}_{ -0.51}$
&
$ -0.10^{  0.26}_{ -0.43}$
&
0
&
$ -0.10^{  0.17}_{ -0.12}$
&
$ -0.58^{  0.28}_{ -0.49}$
\\
$\zeta_{X}$
&
$ 0.012^{ 0.040}_{-0.040}$
&
$-0.002^{ 0.033}_{-0.034}$
&
$-0.032^{ 0.028}_{-0.028}$
&
$-0.014^{ 0.024}_{-0.025}$
&
$-0.029^{ 0.021}_{-0.022}$
\\
${\zeta_X-\zeta_2-1}$
&
$  -0.9^{   0.8}_{  -2.2}$
&
$  -0.7^{   0.5}_{  -1.4}$
&
0
&
$  -0.4^{   0.2}_{  -0.5}$
&
$  -0.1^{   0.5}_{  -0.4}$

\\
${\gamma_X/\gamma_2-1}$
&
$  0.61^{  0.05}_{ -0.05}$
&
$  0.33^{  0.03}_{ -0.03}$
&
0
&
$ -0.23^{  0.01}_{ -0.01}$
&
$ -0.45^{  0.03}_{ -0.03}$
\\
$R_{X}$
&
$  4.93^{  0.52}_{ -0.46}$
&
$  4.06^{  0.43}_{ -0.38}$
&
$  3.06^{  0.34}_{ -0.30}$
&
$  2.35^{  0.28}_{ -0.25}$
&
$  1.67^{  0.23}_{ -0.20}$
\\
${\delta_X/\delta_2-1}$
&
$ -0.45^{  0.17}_{ -0.19}$
&
$ -0.29^{  0.10}_{ -0.11}$
&
0
&
$ -0.05^{  0.05}_{ -0.04}$
&
$ -0.13^{  0.10}_{ -0.08}$
\\
$R_{\delta X}$
&
$ -1.92^{  0.90}_{ -1.30}$
&
$ -2.48^{  0.82}_{ -1.30}$
&
$ -3.48^{  0.90}_{ -1.52}$
&
$ -3.30^{  0.83}_{ -1.42}$
&
$ -3.03^{  0.78}_{ -1.31}$
\\
$\sigma_{X}$
&
$ 0.058^{ 0.012}_{-0.011}$
&
$ 0.030^{ 0.007}_{-0.007}$
&
$ 0.017^{ 0.004}_{-0.007}$
&
$ 0.013^{ 0.006}_{-0.008}$
&
$ 0.042^{ 0.005}_{-0.004}$
\\
\hline
\end{tabular}
\caption{68\% credible Intervals for the Global Fit Parameters including $X_1$ \label{globalx1:tab}}
\end{table}

@@

\color{red}
The extrinsic parameters $\gamma$ attributed to dust are fit for without reference to a specific dust model
we now do so in a fit to the 
model of \citet{1999PASP..111...63F},
assuming the fixed 3693,  4369,  5287,  6319, 7611 \AA\  for the effective wavelengths of the supernova flux through the bands.
Figure~\ref{fitz:fig} shows the   68\% credible intervals of $\gamma$ and our result
$R^F_V=3.06\pm 0.18$.  
We do the analysis in $\gamma$, as opposed to $R_V$ say, because the posteriors of $\gamma$ are well-approximated by a normal distribution that is used for the fit.
\color{black}
